---
title: "LCD Stations"
author: "Caroline Williams"
output:
  prettydoc::html_pretty:
    theme: leonids
    highlight: github
vignette: >
  %\VignetteIndexEntry{LCD Station Data Download}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set cache location
- Update test works
```{r, eval = FALSE}
library(rnoaa)
lcd_cache$cache_path_set(full_path = "D:/noaa_lcd")
lcd("72511814751", 2005)
```

## Download Stations
Note that this download process is still in a testing phase. The function to iterate through downloading station data works, however a station may have a different number depending on the year. Therefore, I plan to either download these csv files into tibbles based on the number of years downloaded, or I will update my lcd_data function to be more flexibble and select the dates for each number. I will then work on sorting and organizing this dataset for my analysis. I also am considering downloading data into my previously defined clusters which includes two from the northeast, one from the northern lake states, and two from the southeast.

### Stations (original values, some stations have multiple numbers)
- "72511814751" - HARRISBURG CAPITAL CITY AIRPORT, PA US
- "72511514711" - MIDDLETOWN HARRISBURG INTERNATIONAL AIRPORT, PA US
- "99999964756" - MILLBROOK 3 W, NY US
- "72520094823" - PITTSBURGH ASOS, PA US
- "72503614757" - POUGHKEEPSIE AIRPORT, NY US
- "72510314712" - READING REGIONAL AIRPORT, PA US
- "72514014778" - SELINSGROVE PENN VALLEY AIRPORT, PA US
- "99999954785" - SOMERSET AIRPORT, NJ US
- "99999954793" - SUSSEX AIRPORT, NJ US
- "72409514792" - TRENTON MERCER AIRPORT, NJ US
- "72427514894" - WHEELING OHIO CO AIRPORT, WV US
- "72513014777" - WILKES BARRE SCRANTON INTERNATIONAL AIRPORT, PA US
- "72514014778" - WILLIAMSPORT REGIONAL AIRPORT, PA US
- "99999954779" - AEROFLEX ANDOVER AIRPORT, NJ US
- "72517014737" - ALLENTOWN LEHIGH VALLEY INTERNATIONAL AIRPORT, PA US
- "99999954782" - HERITAGE FIELD AIRPORT, PA US
- "99999954737" - LANCASTER AIRPORT, PA US 
- "99999954704" - NORWOOD MEMORIAL AIRPORT, MA US
- "72510094746" - WORCESTER, MA US
- "74410414763" - PITTSFIELD MUNICIPAL AIRPORT, MA US
- "99999994994" - BOSCOBEL AIRPORT, WI US
- "99999914702" - BEDFORD HANSCOM FIELD, MA US 
- "72510704780" - FITCHBURG MUNICIPAL AIRPORT, MA US
- "72498894704" - DANSVILLE MUNICIPAL AIRPORT, NY US
- "99999954778" - PENN YAN AIRPORT, NY US
- "99999954768" - NORTH ADAMS HARRIMAN AIRPORT, MA US
- "99999994723" - LAWRENCE MUNICIPAL AIRPORT, MA US
- "72518014735" - ALBANY INTERNATIONAL AIRPORT, NY US
- "72519014771" - SYRACUSE HANCOCK INTERNATIONAL AIRPORT, NY US
- "72529014768" - ROCHESTER GREATER INTERNATIONAL, NY US
- "72518514750" - GLENS FALLS AIRPORT, NY US
- "99999954740" - SPRINGFIELD HARTNESS STATE AIRPORT, VT US
- "99999954773" - FULTON OSWEGO CO AIRPORT, NY US
- "99999954772" - FRYEBURG EASTERN SLOPES REGL AIRPORT, ME US
- "72537094847" - DETROIT METRO AIRPORT, MI US
- "99999994815" - KALAMAZOO BATTLE CREEK INTERNATIONAL AIRPORT, MI US
- "72539514833" - JACKSON REYNOLDS FIELD, MI US
- "72539014836" - LANSING CAPITAL CITY AIRPORT, MI US
- "72637014826" - FLINT FCWOS, MI US
- "72641014837" - MADISON DANE CO REGIONAL AIRPORT, WI US
- "99999954903" - NECEDAH 5 WNW, WI US
- "72638094814" - HOUGHTON LAKE ROSCOMMON CO AIRPORT, MI US
- "72645014898" - GREEN BAY A S INTERNATIONAL AIRPORT, WI US
- "72646314897" - WAUSAU ASOS, WI US
- "72734714841" - PELLSTON REGIONAL AIRPORT, MI US
- "99999994893" - IRON MOUNTAIN FORD AIRPORT, MI US
- "99999994973" - HAYWARD MUNICIPAL AIRPORT, WI US
- "72221513884" - CRESTVIEW BOB SIKES AIRPORT, FL US
- "72216693845" - VALDOSTA REGIONAL AIRPORT, GA US
- "99999963829" - NEWTON 11 SW, GA US
- "99999963828" - NEWTON 8 W, GA US
- "72216013869" - ALBANY SW GEORGIA REGIONAL AIRPORT, GA US
- "72316013870" - ALMA BACON CO AIRPORT, GA US
- "72207003822" - SAVANNAH INTERNATIONAL AIRPORT, GA US
- "72225593842" - COLUMBUS METROPOLITAN AIRPORT, GA US
- "72217003813" - MACON MIDDLE GA REGIONAL AIRPORT, GA US
- "99999953874" - GREENWOOD CO AIRPORT, SC US
- "99999953838" - GAINESVILLE LEE GILMER MEMORIAL AIRPORT, GA US 
- "72320093801" - ROME R B RUSSELL AIRPORT, GA US
- "72319093846" - ANDERSON FAA AIRPORT, SC US
- "99999953850" - CLEMSON OCONEE CO AIRPORT, SC US
- "72311913886" - GREENVILLE DOWNTOWN AIRPORT, SC US
- "72312003870" - GRNVL SPART INTERNATIONAL AIRPORT, SC US
- "99999953870" - GASTONIA MUNICIPAL AIRPORT, NC US
- "72314013881" - CHARLOTTE DOUGLAS AIRPORT, NC US

## Test 1
### Test 1.a
```{r, eval = FALSE}
library(rnoaa)
library(dplyr)
library(tidyr)
library(vctrs)
library(plyr)

# List of LCD stations and their respective station numbers (all stations)
lcd_stat <- list("72511814751", # HARRISBURG CAPITAL CITY AIRPORT, PA US
                 "72511514711", # MIDDLETOWN HARRISBURG INTERNATIONAL AIRPORT, PA US
                 "99999964756", # MILLBROOK 3 W, NY US
                 "72520094823", # PITTSBURGH ASOS, PA US
                 "72503614757", # POUGHKEEPSIE AIRPORT, NY US
                 "72510314712", # READING REGIONAL AIRPORT, PA US
                 "72514014778", # SELINSGROVE PENN VALLEY AIRPORT, PA US
                 "99999954785", # SOMERSET AIRPORT, NJ US
                 "99999954793", # SUSSEX AIRPORT, NJ US
                 "72409514792", # TRENTON MERCER AIRPORT, NJ US
                 "72427514894", # WHEELING OHIO CO AIRPORT, WV US
                 "72513014777", # WILKES BARRE SCRANTON INTERNATIONAL AIRPORT, PA US
                 "72514014778", # WILLIAMSPORT REGIONAL AIRPORT, PA US
                 "99999954779", # AEROFLEX ANDOVER AIRPORT, NJ US
                 "72517014737", # ALLENTOWN LEHIGH VALLEY INTERNATIONAL AIRPORT, PA US
                 "99999954782", # HERITAGE FIELD AIRPORT, PA US
                 "99999954737", # LANCASTER AIRPORT, PA US 
                 "99999954704", # NORWOOD MEMORIAL AIRPORT, MA US
                 "72510094746", # WORCESTER, MA US
                 "74410414763", # PITTSFIELD MUNICIPAL AIRPORT, MA US
                 "99999994994", # BOSCOBEL AIRPORT, WI US
                 "99999914702", # BEDFORD HANSCOM FIELD, MA US 
                 "72510704780", # FITCHBURG MUNICIPAL AIRPORT, MA US
                 "72498894704", # DANSVILLE MUNICIPAL AIRPORT, NY US
                 "99999954778", # PENN YAN AIRPORT, NY US
                 "99999954768", # NORTH ADAMS HARRIMAN AIRPORT, MA US
                 "99999994723", # LAWRENCE MUNICIPAL AIRPORT, MA US
                 "72518014735", # ALBANY INTERNATIONAL AIRPORT, NY US
                 "72519014771", # SYRACUSE HANCOCK INTERNATIONAL AIRPORT, NY US
                 "72529014768", # ROCHESTER GREATER INTERNATIONAL, NY US
                 "72518514750", # GLENS FALLS AIRPORT, NY US
                 "99999954740", # SPRINGFIELD HARTNESS STATE AIRPORT, VT US
                 "99999954773", # FULTON OSWEGO CO AIRPORT, NY US
                 "99999954772", # FRYEBURG EASTERN SLOPES REGL AIRPORT, ME US
                 "72537094847", # DETROIT METRO AIRPORT, MI US
                 "99999994815", # KALAMAZOO BATTLE CREEK INTERNATIONAL AIRPORT, MI US
                 "72539514833", # JACKSON REYNOLDS FIELD, MI US
                 "72539014836", # LANSING CAPITAL CITY AIRPORT, MI US
                 "72637014826", # FLINT FCWOS, MI US
                 "72641014837", # MADISON DANE CO REGIONAL AIRPORT, WI US
                 "99999954903", # NECEDAH 5 WNW, WI US
                 "72638094814", # HOUGHTON LAKE ROSCOMMON CO AIRPORT, MI US
                 "72645014898", # GREEN BAY A S INTERNATIONAL AIRPORT, WI US
                 "72646314897", # WAUSAU ASOS, WI US
                 "72734714841", # PELLSTON REGIONAL AIRPORT, MI US
                 "99999994893", # IRON MOUNTAIN FORD AIRPORT, MI US
                 "99999994973", # HAYWARD MUNICIPAL AIRPORT, WI US
                 "72221513884", # CRESTVIEW BOB SIKES AIRPORT, FL US
                 "72216693845", # VALDOSTA REGIONAL AIRPORT, GA US
                 "99999963829", # NEWTON 11 SW, GA US
                 "99999963828", # NEWTON 8 W, GA US
                 "72216013869", # ALBANY SW GEORGIA REGIONAL AIRPORT, GA US
                 "72316013870", # ALMA BACON CO AIRPORT, GA US
                 "72207003822", # SAVANNAH INTERNATIONAL AIRPORT, GA US
                 "72225593842", # COLUMBUS METROPOLITAN AIRPORT, GA US
                 "72217003813", # MACON MIDDLE GA REGIONAL AIRPORT, GA US
                 "99999953874", # GREENWOOD CO AIRPORT, SC US
                 "99999953838", # GAINESVILLE LEE GILMER MEMORIAL AIRPORT, GA US 
                 "72320093801", # ROME R B RUSSELL AIRPORT, GA US
                 "72319093846", # ANDERSON FAA AIRPORT, SC US
                 "99999953850", # CLEMSON OCONEE CO AIRPORT, SC US
                 "72311913886", # GREENVILLE DOWNTOWN AIRPORT, SC US
                 "72312003870", # GRNVL SPART INTERNATIONAL AIRPORT, SC US
                 "99999953870", # GASTONIA MUNICIPAL AIRPORT, NC US
                 "72314013881") # CHARLOTTE DOUGLAS AIRPORT, NC US

```

#### Identifying stations that are missing certain years of interest
To Do:
- iterate through complete stations first assign a name LCD_stations_2005_2014
- iterate through stations based on year ranges it applies for
  - 2005/ 2006-2014
  - 2008/ 2005-2007 and 2009-2014
  - 2005-2010/ 2011-2014
- pairs of data with different station values
- so need to iterate then bind somehow?
- also need to change cache location data wise


```{r, eval = FALSE}
# Finding which data is present/ absent in the 10 years of interest
# This thesis is already completed. At the time of completion all data was available for all to years
# interestingly, some data is now unavailable

lcd_stat <- list("72511814751", # all 10 years
                 "72511514711", # missing 2011-2014 # try 72399014711
                 "99999964756", # all 10 years
                 "72520094823", # all 10 years
                 "72503614757", # all 10 years
                 "72510314712", # all 10 years
                 "72514014778", # all 10 years
                 "99999954785", # missing 2006-2014 # try 72224754785
                 "99999954793", # missing 2006-2014 # try 74000154793
                 "72409514792", # all 10 years
                 "72427514894", # all 10 years
                 "72513014777", # all 10 years
                 "72514014778", # all 10 years
                 "99999954779", # missing 2006-2014 # try 72407754779
                 "72517014737", # all 10 years
                 "99999954782", # missing 2006-2014 # try 72510954782
                 "99999954737", # missing 2006-2014 # try 72511654737
                 "99999954704", # missing 2006-2014 # try 72509854704
                 "72510094746", # missing 2008 # try 72509594746
                 "74410414763", # missing 2005 # try 99999914763
                 "99999994994", # missing all 10 years # try 72643894994
                 "99999914702", # missing 2006-2014 # try 72505914702
                 "72510704780", # all 10 years
                 "72498894704", # all 10 years
                 "99999954778", # missing 2006-2014 # try 72519454778
                 "99999954768", # missing 2006-2014 # try 72507554768
                 "99999994723", # missing 2006-2014 # try 74490494723
                 "72518014735", # all 10 years
                 "72519014771", # all 10 years
                 "72529014768", # all 10 years
                 "72518514750", # missing 2011-2014 # try 72522014750
                 "99999954740", # missing 2006-2014 # try 72611554740
                 "99999954773", # missing 2006-2014 # try 72514654773
                 "99999954772", # missing 2006-2014 # try 72618354772
                 "72537094847", # all 10 years
                 "99999994815", # missing 2006-2014 # try 72635794815
                 "72539514833", # all 10 years
                 "72539014836", # all 10 years
                 "72637014826", # all 10 years
                 "72641014837", # all 10 years
                 "99999954903", # all 10 years
                 "72638094814", # all 10 years
                 "72645014898", # all 10 years
                 "72646314897", # all 10 years
                 "72734714841", # all 10 years
                 "99999994893", # missing 2006-2014 # try 72743794893
                 "99999994973", # missing 2006-2014 # try 72650894973
                 "72221513884", # missing 2006-2014 # try 72221513884
                 "72216693845", # all 10 years
                 "99999963829", # all 10 years
                 "99999963828", # all 10 years
                 "72216013869", # all 10 years
                 "72316013870", # missing 2008 # try 72213513870
                 "72207003822", # all 10 years
                 "72225593842", # all 10 years
                 "72217003813", # all 10 years
                 "99999953874", # missing 2006-2014 # try 72312453874
                 "99999953838", # missing 2006-2014 # try 72218553838
                 "72320093801", # all 10 years
                 "72319093846", # missing 2008 # try 72312593846
                 "99999953850", # missing 2006-2014 # try 72311853850
                 "72311913886", # all 10 years
                 "72312003870", # all 10 years
                 "99999953870", # missing 2006-2014 # try 72314753870
                 "72314013881") # all 10 years


lcd_cache$cache_path_set(full_path = "D:/noaa_lcd")
lcd_2005_2010 <- list("72511514711", # missing 2011-2014 # try 72399014711
                      "72518514750") # missing 2011-2014 # try 72522014750
                 
lcd_2011_2014 <- list("72399014711", # missing 2011-2014 # try 72399014711
                      "72522014750") # missing 2011-2014 # try 72522014750

lcd_2008 <- list("72509594746", # missing 2008 # try 72509594746
                 "72213513870", # missing 2008 # try 72213513870
                 "72312593846") # missing 2008 # try 72312593846
                 
lcd_200507_200914 <- list("72510094746", # missing 2008 # try 72509594746
                          "72316013870", # missing 2008 # try 72213513870
                          "72319093846") # missing 2008 # try 72312593846

lcd_data(lcd_2005_2010, "2005_2010")
lcd_data(lcd_2011_2014, "2011_2014")
lcd_data(lcd_2008, "2008")
lcd_data(lcd_200507_200914, "200507_200914")
```

### Test 1.b
```{r, eval = FALSE}
library(rnoaa)
library(dplyr)
library(tidyr)
library(vctrs)
library(plyr)

# List of LCD stations and their respective station numbers
lcd_stat <- list("72511814751", # HARRISBURG CAPITAL CITY AIRPORT, PA US
                 "99999964756", # MILLBROOK 3 W, NY US
                 "72520094823", # PITTSBURGH ASOS, PA US
                 "72503614757", # POUGHKEEPSIE AIRPORT, NY US
                 "72510314712", # READING REGIONAL AIRPORT, PA US
                 "72514014778", # SELINSGROVE PENN VALLEY AIRPORT, PA US
                 "72409514792", # TRENTON MERCER AIRPORT, NJ US
                 "72427514894", # WHEELING OHIO CO AIRPORT, WV US
                 "72513014777", # WILKES BARRE SCRANTON INTERNATIONAL AIRPORT, PA US
                 "72514014778", # WILLIAMSPORT REGIONAL AIRPORT, PA US
                 "72517014737", # ALLENTOWN LEHIGH VALLEY INTERNATIONAL AIRPORT, PA US
                 "72510704780", # FITCHBURG MUNICIPAL AIRPORT, MA US
                 "72498894704", # DANSVILLE MUNICIPAL AIRPORT, NY US
                 "72518014735", # ALBANY INTERNATIONAL AIRPORT, NY US
                 "72519014771", # SYRACUSE HANCOCK INTERNATIONAL AIRPORT, NY US
                 "72529014768", # ROCHESTER GREATER INTERNATIONAL, NY US
                 "72537094847", # DETROIT METRO AIRPORT, MI US
                 "72539514833", # JACKSON REYNOLDS FIELD, MI US
                 "72539014836", # LANSING CAPITAL CITY AIRPORT, MI US
                 "72637014826", # FLINT FCWOS, MI US
                 "72641014837", # MADISON DANE CO REGIONAL AIRPORT, WI US
                 "99999954903", # NECEDAH 5 WNW, WI US
                 "72638094814", # HOUGHTON LAKE ROSCOMMON CO AIRPORT, MI US
                 "72645014898", # GREEN BAY A S INTERNATIONAL AIRPORT, WI US
                 "72646314897", # WAUSAU ASOS, WI US
                 "72734714841", # PELLSTON REGIONAL AIRPORT, MI US
                 "72216693845", # VALDOSTA REGIONAL AIRPORT, GA US
                 "99999963829", # NEWTON 11 SW, GA US
                 "99999963828", # NEWTON 8 W, GA US
                 "72216013869", # ALBANY SW GEORGIA REGIONAL AIRPORT, GA US
                 "72207003822", # SAVANNAH INTERNATIONAL AIRPORT, GA US
                 "72225593842", # COLUMBUS METROPOLITAN AIRPORT, GA US
                 "72217003813", # MACON MIDDLE GA REGIONAL AIRPORT, GA US
                 "72320093801", # ROME R B RUSSELL AIRPORT, GA US
                 "72311913886", # GREENVILLE DOWNTOWN AIRPORT, SC US
                 "72312003870", # GRNVL SPART INTERNATIONAL AIRPORT, SC US
                 "72314013881") # CHARLOTTE DOUGLAS AIRPORT, NC US


```

## Test 2
```{r, eval = FALSE}
# Here is a test example of looping through stations for all 10 years
# The output is a list of three tibbles corresponding to each input station
stat_name <- list("HARRISBURG_CAPITAL_CITY_AIRPORT_PA",
                  "MILLBROOK_3_W_NY",
                  "PITTSBURGH ASOS_PA")
                 
lcd_test <- list("72511814751", 
                 "99999964756", 
                 "72520094823")




# Testing merging station data
lcd_stat_2005 <- list("99999954785")
lcd_stat_2006_2014 <- list("72224754785")

lcd_data_2005 <- lapply(lcd_stat_2005, function(x) {
  as_tibble(rbind.fill(lcd(x, year = 2005)))
})

lcd_data_2006_2014 <- lapply(lcd_stat_2006_2014, function(x) {
  as_tibble(rbind.fill(lcd(x, year = 2006),
                       lcd(x, year = 2007),
                       lcd(x, year = 2008),
                       lcd(x, year = 2009),
                       lcd(x, year = 2010),
                       lcd(x, year = 2011),
                       lcd(x, year = 2012),
                       lcd(x, year = 2013),
                       lcd(x, year = 2014)))
})
#combine afterword
# perhaps make into a missing values function

test <- rbind.fill(lcd_data_2005, lcd_data_2006_2014)
# Considering using paste0 to name each tibble somehow
t <- m_test[[1]]
paste0("LCD_", stat_name[[1]], "_2005_2014")

# Trying different methods of sorting data
# To DO: try using pivot_wider to split date into year and month
# then calculate the mean ofjuly over the 10 years per station
# output to a single tibble file

LCD_new <- as_tibble(m_test[[1]]) 
LCD_new %>% select(station, date, latitude, longitude, elevation, name, monthlymaximumtemperature, monthlymeantemperature,monthlyminimumtemperature) %>% arrange(monthlymaximumtemperature, monthlymeantemperature,monthlyminimumtemperature)

LCD_new %>% select(station, date, latitude, longitude, elevation, name, monthlymaximumtemperature, monthlymeantemperature,monthlyminimumtemperature) %>% arrange(desc(date))

LCD_degrees <- LCD_new %>% select(station, date, latitude, longitude, elevation, name, monthlymaximumtemperature, monthlymeantemperature,monthlyminimumtemperature) %>% filter(monthlymeantemperature > 0)

LCD_degrees %>% summarize_all(mean(monthlymaximumtemperature, monthlymeantemperature,monthlyminimumtemperature))
```

## Clusters
### 2005 to 2014
```{r}
# Creating lists by cluster for the years 2005 to 2014
NE1_2005_2014 <- list("72510704780", # all 10 years
                      "72498894704", # all 10 years
                      "72518014735", # all 10 years
                      "72519014771", # all 10 years
                      "72529014768") # all 10 years
                      
NE2_2005_2014 <- list()
NLS_2005_2014 <- list()
SE1_2005_2014 <- list()
SE2_2005_2014 <- list()

# Downloading stations by cluster for 2005 to 2014
NE1_2005_2014_data <- lcd_data(NE1_2005_2014, "2005_2014")
lcd_data(NE2_2005_2014, "2005_2014")
lcd_data(NLS_2005_2014, "2005_2014")
lcd_data(SE1_2005_2014, "2005_2014")
lcd_data(SE2_2005_2014, "2005_2014")
```

### 2005
```{r}
# Creating lists by cluster for the year 2005
NE1_2005 <- list("99999954704", # missing 2006-2014 # try 72509854704 
                 "99999914763", # missing 2005 # try 99999914763
                 "99999914702", # missing 2006-2014 # try 72505914702
                 "99999954778", # missing 2006-2014 # try 72519454778
                 "99999954768", # missing 2006-2014 # try 72507554768
                 "99999994723", # missing 2006-2014 # try 74490494723
                 "99999954740", # missing 2006-2014 # try 72611554740
                 "99999954773", # missing 2006-2014 # try 72514654773
                 "99999954772") # missing 2006-2014 # try 72618354772
                      
NE2_2005 <- list()
NLS_2005 <- list()
SE1_2005 <- list()
SE2_2005 <- list()

# Downloading stations by cluster for 2005
NE1_2005_data <- lcd_data(NE1_2005, "2005")
lcd_data(NE2_2005, "2005")
lcd_data(NLS_2005, "2005")
lcd_data(SE1_2005, "2005")
lcd_data(SE2_2005, "2005")
```

### 2006 to 2014
```{r}
# Creating lists by cluster for the years 2006 to 2014
NE1_2006_2014 <- list("72509854704", # missing 2006-2014 # try 72509854704 
                      "72509854704", # missing 2005 # try 99999914763
                      "72505914702", # missing 2006-2014 # try 72505914702
                      "72519454778", # missing 2006-2014 # try 72519454778
                      "72507554768", # missing 2006-2014 # try 72507554768
                      "74490494723", # missing 2006-2014 # try 74490494723
                      "72611554740", # missing 2006-2014 # try 72611554740
                      "72514654773", # missing 2006-2014 # try 72514654773
                      "72618354772") # missing 2006-2014 # try 72618354772
                      
NE2_2006_2014 <- list()
NLS_2006_2014 <- list()
SE1_2006_2014 <- list()
SE2_2006_2014 <- list()

# Downloading stations by cluster for 2006 to 2014
NE1_2006_2014_data <- lcd_data(NE1_2006_2014, "2006_2014")
lcd_data(NE2_2006_2014, "2006_2014")
lcd_data(NLS_2006_2014, "2006_2014")
lcd_data(SE1_2006_2014, "2006_2014")
lcd_data(SE2_2006_2014, "2006_2014")
```

### 2008
```{r}
# Creating lists by cluster for the year 2008
NE1_2008 <- list("72509594746") # missing 2008 # try 72509594746
                      
NE2_2008 <- list()
NLS_2008 <- list()
SE1_2008 <- list()
SE2_2008 <- list()

# Downloading stations by cluster for 2008
NE1_2008_data <- lcd_data(NE1_2008, "2008")
lcd_data(NE2_2008, "2008")
lcd_data(NLS_2008, "2008")
lcd_data(SE1_2008, "2008")
lcd_data(SE2_2008, "2008")
```

### 2005 to 2007 and 2009 to 2014
```{r}
# Creating lists by cluster for the years 2005 to 2007 and 2009 to 2014
NE1_200507_200914 <- list("72510094746") # missing 2008 # try 72509594746
                      
NE2_200507_200914 <- list()
NLS_200507_200914 <- list()
SE1_200507_200914 <- list()
SE2_200507_200914 <- list()

# Downloading stations by cluster for 2005 to 2014
NE1_200507_200914_data <- lcd_data(NE1_200507_200914, "200507_200914")
lcd_data(NE2_200507_200914, "200507_200914")
lcd_data(NLS_200507_200914, "200507_200914")
lcd_data(SE1_200507_200914, "200507_200914")
lcd_data(SE2_200507_200914, "200507_200914")
```

### 2005 to 2010
```{r}
# Creating lists by cluster for the years 2005 to 2010
NE1_2005_2010 <- list("72518514750") # missing 2011-2014 # try 72522014750
                    
                      
NE2_2005_2010 <- list()
NLS_2005_2010 <- list()
SE1_2005_2010 <- list()
SE2_2005_2010 <- list()

# Downloading stations by cluster for 2005 to 2014
NE1_2005_2010_data <- lcd_data(NE1_2005_2010, "2005_2010")
lcd_data(NE2_2005_2010, "2005_2010")
lcd_data(NLS_2005_2010, "2005_2010")
lcd_data(SE1_2005_2010, "2005_2010")
lcd_data(SE2_2005_2010, "2005_2010")
```

### 2011 to 2014
```{r}
# Creating lists by cluster for the years 2011 to 2014
NE1_2011_2014 <- list("72522014750") # missing 2011-2014 # try 72522014750
                      
NE2_2011_2014 <- list()
NLS_2011_2014 <- list()
SE1_2011_2014 <- list()
SE2_2011_2014 <- list()

# Downloading stations by cluster for 2005 to 2014
NE1_2011_2014_data <- lcd_data(NE1_2011_2014, "2011_2014")
lcd_data(NE2_2011_2014, "2011_2014")
lcd_data(NLS_2011_2014, "2011_2014")
lcd_data(SE1_2011_2014, "2011_2014")
lcd_data(SE2_2011_2014, "2011_2014")
```

## Merging Data
```{r}
# NE1
NE1_merge1 <- mapply(rbind,NE1_2005_data,NE1_2006_2014_data,SIMPLIFY=FALSE)
NE1_merge2 <- mapply(rbind,NE1_2008_data,NE1_200507_200914_data,SIMPLIFY=FALSE)
NE1_merge3 <- mapply(rbind,NE1_2005_2010_data,NE1_2011_2014_data,SIMPLIFY=FALSE)
```

