---
title: "NLCD Raster Download"
author: "Caroline Williams"
output:
  prettydoc::html_pretty:
    theme: leonids
    highlight: github
vignette: >
  %\VignetteIndexEntry{NLCD Raster Data Download}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## NLCD
The NLCD is stored as a GeoTIFF with a spatial resolution of 30 by 30 meters. It is projected in North American Continental Albers and formatted as ENVI-header flat binary raster files. Land cover classes include open water (11), perennial ice/ snow (12), developed open space (21), developed low intensity (22), developed med intensity (23), developed high intensity (24), barren (31), deciduous forest (41), evergreen forest (42), mixed forest (43), dwarf scrub (51), shrubland (52), grassland (71), sedge (72), lichens (73), moss (74), pasture (81), rowcrops (82), woody wetlands (90), and emergent wetlands (95) (Kennedy et al., 2018).

## Download National Land Cover Dataset (NLCD)
The following code is used to iterate through NLCD data (downloaded from: ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/) .zip files. The for loop downloads each .zip file, unzips it, and deletes the original .zip file folder. This is accomplished for the years 2005 to 2014. The packages FedData, sp, utils, and raster are used.

```{r, eval = FALSE}
# Load Packages
library(FedData)
library(sp)
library(utils)
library(raster)

# NLCD urls for landcover vote data for 2005 to 2014
urls <- list("ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/landcover_2005_vote.zip",
             "ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/landcover_2006_vote.zip",
             "ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/landcover_2007_vote.zip",
             "ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/landcover_2008_vote.zip",
             "ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/landcover_2009_vote.zip",
             "ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/landcover_2010_vote.zip",
             "ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/landcover_2011_vote.zip",
             "ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/landcover_2012_vote.zip",
             "ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/landcover_2013_vote.zip",
             "ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/landcover_2014_vote.zip")

nlcd_dir <- "D:/data" # specify the file path for the output NLCD raster data output

# iterate through .zip files downloading landcover data for CONUS
for (i in urls) {
  tmp <- tempfile(tmpdir = nlcd_dir, fileext = ".zip")
  download.file(i, tmp)
  unzip(tmp,exdir = nlcd_dir)
  unlink(tmp)
  fp <- list.files(path = nlcd_dir, full.names = TRUE, pattern = "nlcd_vote")
  fp <- gsub("/", "\\\\", fp)
}
```
