---
title: "NLCD Raster Download"
author: "Caroline Williams"
output:
  prettydoc::html_pretty:
    theme: leonids
    highlight: github
vignette: >
  %\VignetteIndexEntry{NLCD Raster Data Download}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## NLCD
The NLCD is stored as a GeoTIFF with a spatial resolution of 30 by 30 meters. It is projected in North American Continental Albers and formatted as ENVI-header flat binary raster files. Land cover classes include open water (11), perennial ice/ snow (12), developed open space (21), developed low intensity (22), developed med intensity (23), developed high intensity (24), barren (31), deciduous forest (41), evergreen forest (42), mixed forest (43), dwarf scrub (51), shrubland (52), grassland (71), sedge (72), lichens (73), moss (74), pasture (81), rowcrops (82), woody wetlands (90), and emergent wetlands (95) (Kennedy et al., 2018).

## Download National Land Cover Dataset (NLCD)
The following code is used to iterate through [NLCD data](ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/) .zip files. The for loop downloads each .zip file, unzips it, and deletes the original .zip file folder. This is accomplished for the years 2005 to 2014. The packages FedData, sp, utils, and raster are used.

```{r}
# Load Libraries
library(FedData)
library(sp)
library(utils)
library(raster)
library(geospaar)
```

```{r, eval = FALSE}
# NLCD urls for landcover vote data for 2005 to 2014
urls <- list("ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/landcover_2005_vote.zip",
             "ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/landcover_2006_vote.zip",
             "ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/landcover_2007_vote.zip",
             "ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/landcover_2008_vote.zip",
             "ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/landcover_2009_vote.zip",
             "ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/landcover_2010_vote.zip",
             "ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/landcover_2011_vote.zip",
             "ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/landcover_2012_vote.zip",
             "ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/landcover_2013_vote.zip",
             "ftp://islay.ceoas.oregonstate.edu/cms/v1/landcover/vote/landcover_2014_vote.zip")

nlcd_dir <- "D:/data" # specify the file path for the output NLCD raster data output

# iterate through .zip files downloading landcover data for CONUS
for (i in urls) {
  tmp <- tempfile(tmpdir = nlcd_dir, fileext = ".zip")
  download.file(i, tmp)
  unzip(tmp,exdir = nlcd_dir)
  unlink(tmp)
  fp <- list.files(path = nlcd_dir, full.names = TRUE, pattern = "nlcd_vote")
  fp <- gsub("/", "\\\\", fp)
}
```

## Raster Testing
To do:
- read in 2006-2014
- make raster stack 
- do this for other clusters

### Read in Raster
```{r}
# read in raw raster image
nlcd_2005 <- raster("D:/data/landcover_2005_vote.tif")
```

## Project and Crop to NE1 Extent
```{r}
# create sf object of NE1 tibble
NE1_sf <- st_as_sf(NE1_summary, coords = c("longitude", "latitude"), crs = 4326) 

# reproject to crs of nlcd images
NE1_sf <- NE1_sf %>% st_transform(., st_crs(nlcd_2005))

write_sf(NE1_sf, dsn = "D:/r_outputs/NE1_pts.shp")

# define the spatial extent of the stations
NE1_extent <- extent(NE1_sf)

# crop to NE1 extent
nlcd_2005_crop = crop(nlcd_2005, NE1_extent)
```

### Reclass Raster
```{r}
# Land cover classes
nlcdclassname <-  c('Open Water','Perennial Ice/Snow', 'Developed, Open Space',
    'Developed, Low Intensity','Developed, Medium Intensity','Developed High Intensity',
    'Barren Land','Deciduous Forest','Evergreen Forest','Mixed Forest',
    'Dwarf Scrub','Shrub/Scrub','Grassland/Herbaceous','Sedge/Herbaceous',
    'Lichens','Moss','Pasture/Hay','Cultivated Crops','Woody Wetlands',
    'Emergent Herbaceous Wetlands')

# Defining Colors
navy = rgb(0/255,0/255,204/255)
brown = rgb(153/255,76/255,0/255)
ltbrown = rgb(204/255,102/255,0/255)
ltbrown1.2 = rgb(204/255*1.2,102*1.2/255,0/255*1.2)
black = rgb(0/255,0/255,0/255)
white = rgb(1/255,1/255,1/255)
gray1.2 = rgb(.5/255*1.2,.5/255*1.2,.5/255*1.2)
gray1 = rgb(.5/255,.5/255,.5/255)
gray.8 = rgb(.5/255*0.8,.5/255*0.8,.5/255*0.8)
gray.5 = rgb(.5/255*0.5,.5/255*0.5,.5/255*0.5)
orange = rgb(255/255,165/255,0/255)
ltorange = rgb(255/255,153/255,51/255)
ltblue = rgb(173/255,216/255,230/255)
ltblue.8 = rgb(173/255*0.8,216/255*0.8,230/255*0.8)
magenta = rgb(255/255,0/255,255/255)
yellow = rgb(255/255,255/255,0/255)
ltyellow = rgb(255/255,255/255,102/255)
darkgreen = rgb(0/255,102/255,0/255)
brightgreen = rgb(51/255, 255/255, 51/255)
ltgreen = rgb(178/255,255/255,102/255)
medgreen = rgb(76/255,153/255,0/255)
veryltgreen = rgb(204/255,255/255,205/255)
medltgreen =  rgb(204/255,255/255,153/255)
mauve = rgb(153/255,153/255,0/255)

nlcd_col <- c(navy, white, gray1.2,
    gray1, gray.8, gray.5,
    brown, ltgreen, darkgreen, medgreen,
    ltbrown1.2, ltbrown, ltyellow, mauve,
    veryltgreen, medltgreen, yellow, magenta, ltblue.8, ltblue)

# plot mean temperature
plot_noaxes(nlcd_2005_crop, legend = FALSE, main = "NLCD 2005 Data", col = 
              nlcd_col,
            mar = c(1, 1, 2, 1))
legend(x = "right", legend = nlcdclassname, 
       pch = 15, pt.cex = 3, col = nlcd_col, bty = "n")
```
